Missing years 2019 and 2020^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-04-24 outputs/paper/paper.Rmd
Discussion writing (1)

Second, let's explore into the negative group: Figure \@ref(fig:fig1), Figure \@ref(fig:fig2), Figure \@ref(fig:fig4), Figure \@ref(fig:fig11), and Figure \@ref(fig:fig14).
They all show increase in "Too much". There were few things that presented very interesting results. One was health part. It is true that majority answered "Too little" for national spending on healthcare in both years. However, it dropped by 5.8%. Although this is little above from the standard of change I set in the model session, and the variable did not fit into the group, considering 2020 when the survey was conducted, it was surprising. According to Forbes, critical care beds per capita in U.S is the highest among many countries. In other words, unlike other countries, U.S was comparatively able to handle serious patients well. Also, as the pandemic went on, the virus got weaker, which enabled people to treat themselves at home. I suspect that this is why there was drop in "Too little". Therefore, health must stay in the negative group. In addition to the health part, race presented very interesting result as well. Black Lives Matter was a big issue during 2020, however, voice for more actions dropped over the years. It is absolutely true that there should not be any discrimination against races. However, violence cannot be justified under the name of equality. After George Floyd was murdered by a police officer in May 25, 2020, serious riots and looting occurred all over U.S. I think the drop in "Too little" was occured as a counteraction of the violence. The rest variables make sense if you think of the pandemic situation. During the pandemic, not only vaccines were more needed than guns, but taking care of own nation came first than helping other countries. Therefore, it is natural to observe the negative in arms, foreign aids and big city problems.

@@

# Discussion

## Summary

>>>>

Second, let's explore into the negative group: Figure \@ref(fig:fig1), Figure \@ref(fig:fig2), Figure \@ref(fig:fig4), Figure \@ref(fig:fig11), and Figure \@ref(fig:fig14).
They all show increase in "Too much". There were few things that presented very interesting results. One was health part. It is true that majority answered "Too little" for national spending on healthcare in both years. However, it dropped by 5.8%. Although this is little above from the standard of change I set in the model session, and the variable did not fit into the group, considering 2020 when the survey was conducted, it was surprising. According to Forbes, critical care beds per capita in U.S is the highest among many countries. In other words, unlike other countries, U.S was comparatively able to handle serious patients well. Also, as the pandemic went on, the virus got weaker, which enabled people to treat themselves at home. I suspect that this is why there was drop in "Too little". Therefore, health must stay in the negative group. In addition to the health part, race presented very interesting result as well. Black Lives Matter was a big issue during 2020, however, voice for more actions dropped over the years. It is absolutely true that there should not be any discrimination against races. However, violence cannot be justified under the name of equality. After George Floyd was murdered by a police officer in May 25, 2020, serious riots and looting occurred all over U.S. I think the drop in "Too little" was occurred as a counteraction of the violence. The rest variables make sense if you think of the pandemic situation. During the pandemic, not only vaccines were more needed than guns, but taking care of own nation came first than helping other countries. Therefore, it is natural to observe the negative in arms, foreign aids and big city problems.

@@

# Discussion
In this session, we are going to explore remained and unanswered questions from results session.

## Summary
Throughout this paper, we have figured out U.S citizens' various responses regarding their government specifically between 2018 and 2021. By focusing on COVID-19 influences along with backgrounds, I have found out three responses: positive, negative and unchanged. For positive response, variables were collected with respect to changes moved to "Too little" or "About right" in national spending levels. I have observed that strict COVID-19 sanctions or ripple effects from the sanctions affected the thoughts on national spending levels on drug, Welfare and actions on equalizing income differences. Furthermore, the change in drug presented that potential indifference existing in U.S citizens minds. For negative response, variables were collected regarding changes moved to "Too much". I have figured out that the government successfuly dealt with the pandemic regarding healthcare, and nationalism took great deal of explanation for negative responses. Lastly, unchanged variables were mostly related to essential services such as road and education. Also, unexpectedly outdoor services dodged the ripple effects of the sanction.
